Dark Control: The Default Mode Network as a Reinforcement Learning Agent

### 2018-08-08 paper/paper.tex
sentence with 'bootstrap' in section 4 negated

would remain trapped in this location
because its sensory inputs are perfectly predictable
given the environmental state \citep{darkroom2012}.
% \begin{wrapfigure}{r}{.37\linewidth}
%   \centering
%   \includegraphics[width=1.\linewidth]{darkroom_resized.png}
%   \caption{\textbf{The dark room experiment.} An intelligent agent situated
%   in a light-deprived closed space is used
%   as a thought experiment for the complete absence
%   of external sensory input.
%   % The free-energy principle theory paradoxally predicts that such an agent would remain quietly in this room, such it perfectly predict all sensory input from such an environment.
%   % However such behavior is not observed in humans or any animals: the agent would strive to leave such an environment in search of more ``interesting'' worlds.
%   }
%   \label{fig:darkroom}
% \end{wrapfigure}
However, such a behavior is seldom observed in humans in the
real world. In a dark room, the intelligent agents would search for light sources by explore
the surroundings or aim to exit the room.
Defenders of the FEP have retorted by advancing the ``full package'' \citep{darkroom2012}:
FEP is framed as being multi-scale, and there would be one scale at which
the organism would
be \textit{surprised} by a \textit{lack of surprise}.
One may object that a dark room would paradoxically correspond to a state of particularly high relevance.
Driven by the surprise-minimization objective, the FEP agent would eventually bootstrap itself out of such saddle points to explore more interesting parts of the environment.
% Recourse to this argument is equivalent to invoking a \textit{halting oracle}\citep{haltingoracle}, an arbitrarily powerful machine which can solve the \textit{halting problem} (an arbitrarily difficult computational problem which cannot be solved under any reasonable \textit{model of computation}, not even in principle!). But this is problematic as it sucks up the problem (that of decision-making and active agency) the theory intends to elude in the first place.
In contrast, an organism operating under our RL-based theory would inevitably
identify the sensory-stimulus-deprived room as a local minimum. Indeed, hippocampal experience replay (see \ref{sec:self}) could serve to sample memories or fantasies of alternative situations
with reward structure. Such artificially generated \textit{internal} sensory input,
potentially subserved by the DMN, could then entice the organism to explore the room,
for instance by looking for and using the light switch or finding the room exit.

>>>>

would remain trapped in this location
because its sensory inputs are perfectly predictable
given the environmental state \citep{darkroom2012}.
% \begin{wrapfigure}{r}{.37\linewidth}
%   \centering
%   \includegraphics[width=1.\linewidth]{darkroom_resized.png}
%   \caption{\textbf{The dark room experiment.} An intelligent agent situated
%   in a light-deprived closed space is used
%   as a thought experiment for the complete absence
%   of external sensory input.
%   % The free-energy principle theory paradoxally predicts that such an agent would remain quietly in this room, such it perfectly predict all sensory input from such an environment.
%   % However such behavior is not observed in humans or any animals: the agent would strive to leave such an environment in search of more ``interesting'' worlds.
%   }
%   \label{fig:darkroom}
% \end{wrapfigure}
However, such a behavior is seldom observed in humans in the
real world. In a dark room, the intelligent agents would search for light sources by explore
the surroundings or aim to exit the room.
Defenders of the FEP have retorted by advancing the ``full package'' \citep{darkroom2012}:
FEP is framed as being multi-scale, and there would be one scale at which
the organism would
be \textit{surprised} by a \textit{lack of surprise}.
One may object that a dark room would paradoxically correspond to a state of particularly high relevance.
Driven by the surprise-minimization objective, the FEP agent would eventually not bootstrap itself out of such saddle points to explore more interesting parts of the environment.
% Recourse to this argument is equivalent to invoking a \textit{halting oracle}\citep{haltingoracle}, an arbitrarily powerful machine which can solve the \textit{halting problem} (an arbitrarily difficult computational problem which cannot be solved under any reasonable \textit{model of computation}, not even in principle!). But this is problematic as it sucks up the problem (that of decision-making and active agency) the theory intends to elude in the first place.
In contrast, an organism operating under our RL-based theory would inevitably
identify the sensory-stimulus-deprived room as a local minimum. Indeed, hippocampal experience replay (see \ref{sec:self}) could serve to sample memories or fantasies of alternative situations
with reward structure. Such artificially generated \textit{internal} sensory input,
potentially subserved by the DMN, could then entice the organism to explore the room,
for instance by looking for and using the light switch or finding the room exit.
